A Road Segment Prioritization Approach for Cycling Infrastructure

### 2023-04-24 README.Rmd
Tweak prose in intro

The 2015 Paris agreement [@agreement2015paris] acknowledged that
fundamental changes to societies and economies are necessary to mitigate
climate change. Like other sectors, transport is under substantial
pressure to decarbonise, resulting in a number of technical innovations
including electric vehicles. But new vehicle technologies can only go so
far and do not tackle parallel problems such as congestion, road traffic
casualties and physical inactivity [@brand_climate_2020].

In this context, interest and investment in active modes are growing.
The benefits extend beyond congestion and the environment, as active
travel can also help alleviate what is referred to as the pandemic of
global inactivity; physical inactivity is on the rise and has become the
4th highest cause of death globally [@kohl2012pandemic]. Various
studies have documented the association between active transport and
lower risk of disease, including cancer and cardiovascular disease
[@celis2017association; @jarrett2012effect;
@patterson2020associations]. In the wake of the Covid-19 pandemic, and
the resulting reduced capacity of public transport, the UK government
has pledged to invest billions of pounds to improve walking and cycling
infrastructure across the country. While this unprecedented sum is an
opportunity to reshape cities in a way that improves the well-being of
citizens, it does come with a warning:

@@

The funding on its own is therefore no guarantee of a change in
commuting across the country; it must be used to design adequate cycling
infrastructure that is based on motivators and deterrents to cycling. In this paper we 
propose an approach for planning a connected cycling network that is meant to 
be applicable to any city (as shown in the Appendix), and we use the city of Manchester as a case study. Greater 
Manchester aims to become the first region to reach a carbon neutral transport network; 
its local authorities have developed plans for a 1800 mile walking and cycling network 
(Bee Network) that will be delivered over 10 years [@manchestercyclingbee2020]. While schemes 
have already been put in place for around a quarter of this network, the majority is yet to be built.

@@

# Method and Application

## Method overview

@@

Our work builds on these community finding approaches by proposing a
similar greedy network expansion algorithm for cycle network expansion
*within communities*. We incorporate community finding methods for study
area partitioning with weighted routing to avoid links that are
stressful to cycle on. In doing so, we propose an approach that ensures a better distribution 
investments across the study area while also accounting for motivators and deterrents to cycling. 
We propose three sub-methods that address some of the limitations of previous
studies. These limitations include (a) an inherent bias when basing network
design solely on existing cycling demand, (b) the proposal of routes that may
not correspond to studies on cyclist preference and government policies,
and (c) an insufficient consideration of the ethical principles underlying
the analysis. The current work addresses these limitations through the following organisation. Section \@ref(calculating-potential-cycling-demand)
focuses on calculating potential cycling demand. Section \@ref(routing)
focuses on routing the demand onto the road network while accounting for
cyclist preferences and government priorities. Section
\@ref(road-segment-prioritization) outlines a method for partitioning the
study area based on a community finding algorithm and routed cycling
demand. It then introduces the network expansion algorithms, and compares an approach grounded in
'egalitarianism' to one grounded in 'utilitarianism'. As mentioned above, Manchester is used as a case study. 
An overview of the steps involved is shown in Figure \@ref(fig:methodflowchart).

```{r methodflowchart, fig.cap="Flowchart of proposed methodology", out.width="80%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("extras/methodology_flowchart.png")
```

## Calculating Potential Cycling Demand

@@

## Routing

@@

## Road Segment Prioritization

@@

### Community Detection

@@

### Algorithm 1: Utilitarian Expansion

@@

### Algorithm 2: Egalitarian Expansion

@@

### Connectivity

>>>>

The 2015 Paris agreement [@agreement2015paris] acknowledged that
fundamental changes to societies and economies are necessary to mitigate
climate change. Like other sectors, transport is under substantial
pressure to decarbonise, resulting in a number of technical innovations
including electric vehicles. But new vehicle technologies can only go so
far and fail to tackle parallel problems such as congestion, road traffic
casualties and physical inactivity [@brand_climate_2020].

In this context, interest and investment in active modes has grown substantially, especially with the growing realisation that the benefits extend beyond congestion and the environment, as active
travel can also help alleviate what is referred to as the pandemic of
global inactivity; physical inactivity is on the rise and has become the
4th highest cause of death globally [@kohl2012pandemic]. Various
studies have documented the association between active transport and
lower risk of disease, including cancer and cardiovascular disease
[@celis2017association; @jarrett2012effect; @patterson2020associations]. In the wake of the Covid-19 pandemic, and
the resulting reduced capacity of public transport, the UK government
has pledged to invest billions of pounds to improve walking and cycling
infrastructure across the country. While this unprecedented sum is an
opportunity to reshape cities in a way that improves the well-being of
citizens, it does come with a warning:

@@

Funding alone is therefore no guarantee of a change in
commuting across the country; it must be used to design adequate cycling
infrastructure that is based on motivators and deterrents to cycling. In this paper we 
propose an approach for planning a connected cycling network that is meant to 
be applicable to any city (as shown in the Appendix), and we use the city of Manchester as a case study. Greater 
Manchester aims to become the first region to reach a carbon neutral transport network; 
its local authorities have developed plans for a 1800 mile walking and cycling network 
(Bee Network) that will be delivered over 10 years [@manchestercyclingbee2020]. While schemes 
have already been put in place for around a quarter of this network, the majority is yet to be built.

@@

@@

<!-- EDIT! Add more to limitations -->

Our work builds on these community finding approaches by proposing a
similar greedy network expansion algorithm for cycle network expansion
*within communities*. We incorporate community finding methods for study
area partitioning with weighted routing to avoid links that are
stressful to cycle on. In doing so, we propose an approach that ensures a better distribution 
investments across the study area while also accounting for motivators and deterrents to cycling. 
We propose three sub-methods that address some of the limitations of previous
studies. These limitations include (a) an inherent bias when basing network
design solely on existing cycling demand, (b) the proposal of routes that may
not correspond to studies on cyclist preference and government policies,
and (c) an insufficient consideration of the ethical principles underlying
the analysis. The current work addresses these limitations through the following organisation. Section \@ref(calculating-potential-cycling-demand)
focuses on calculating potential cycling demand. Section \@ref(routing)
focuses on routing the demand onto the road network while accounting for
cyclist preferences and government priorities. Section
\@ref(road-segment-prioritization) outlines a method for partitioning the
study area based on a community finding algorithm and routed cycling
demand. It then introduces the network expansion algorithms, and compares an approach grounded in
'egalitarianism' to one grounded in 'utilitarianism'.

# Calculating Potential Cycling Demand

@@

# Routing

@@

# Road Segment Prioritization

@@

## Community Detection

@@

## Algorithm 1: Utilitarian Expansion

@@

## Algorithm 2: Egalitarian Expansion

@@

## Connectivity
